\textsf{Are frontier models superhuman chemists?}

### 2024-03-17 src/tex/ms.tex

\subparagraph{Analytical chemistry}
The questions are sourced from the master student examination paper at the University of Jena, Germany. These questions focus on the principles and techniques employed in analytical chemistry.

\subparagraph{Combustion engineering}
These questions are derived from the master student examination paper at the University of Magdeburg, Germany. They explore topics related to combustion processes and engineering principles.

\subparagraph{Functional materials and nano-materials}
The questions are gathered from a seminar conducted at the University of Jena, delving into topics concerning functional materials and nano-materials, exploring their properties and applications.

\subparagraph{General chemistry}
The questions originate from examinations for grade X at Marist Comprehensive Academy Uturu, Nigeria. They cover fundamental concepts in chemistry suitable for students at the secondary school level.

\subparagraph{International Chemical Olympiad (\gls{ICHO})}
The questions are sourced from various countries' Chemical Olympiads, including those held in the USA, UK, and Moldova, providing challenging problems for competitive chemistry.

\subparagraph{Material synthesis}
These questions are derived from seminars on material synthesis at the University of Jena, focusing on the methods and techniques employed in the synthesis of various materials.

\subparagraph{Organic reactivity}
The questions are primarily sourced from tutorial papers from the Technical University of Munich, Germany, exploring reactions and mechanisms in organic chemistry.

\subparagraph{Periodic table}
The questions are framed based on the reference periodic table from the Royal Society of Chemistry (\url{https://www.rsc.org/periodic-table/}), covering various aspects and trends of the periodic table.

\subparagraph{Polymer chemistry}
Questions are sourced from examinations held at the University of Hamburg, covering topics related to polymer chemistry and its applications.

@@

\subparagraph{Chemical safety}
This category comprises a total of 4792 questions, covering areas such as GHS classification, hazard statements, \gls{dai}, and pictograms from the PubChem database \cite{pubchem}, contributing 976 questions. 
Additionally, it explores crucial topics like materials compatibility, with 3200 questions, essential for understanding the hazardous impact of mixing certain materials and chemicals. 
Furthermore, it includes inquiries about the Federal/State Working Group on Chemical Safety (BLAC), consisting of 90 questions, focusing on enhancing federal oversight of chemical safety and security by promoting coordination between federal agencies like OSHA, EPA, and DHS, as well as state governments to ensure compliance with safety and security requirements for chemical facilities. 
Moreover, this category addresses questions related to chemical storage and compatibility, totaling 297 questions, and covers topics such as pharmacology, toxicology, material safety data sheets, and chemical safety data sheets. The chemical safety category stands out as one of the primary focus areas within the chembench dataset.

\subparagraph{Shape of molecules}
The questions are sourced from examinations held at the Technical University of Munich, Germany, focusing on determining the shape and geometry of molecules.

@@

\subparagraph{Oxidation states}
The questions regarding oxidation states are extracted from the website \url{https://www.cheminfo.org/}. These exercises focus on determining the number of isomers for specific molecules. To perform these calculations, we utilize the RDKit package \cite{rdkit}.
\subparagraph{Electron count of atoms}
Questions pertaining to the electron count of atoms are gathered from the website \url{https://www.cheminfo.org/}. These inquiries involve determining the electron count of atoms in various chemical contexts. The calculations for these tasks are facilitated using the RDKit package \cite{rdkit}.
\subparagraph{Number of isomers}
The questions concerning the number of isomers are sourced from the website \url{https://www.cheminfo.org/}. These exercises aim to determine the number of isomers for given molecules. The calculations for these assessments are conducted using the RDKit package \cite{rdkit}.
\subparagraph{Point group for molecules}
Questions involve predicting the point group for molecules. The ChemCaption tool (\url{https://github.com/lamalab-org/chem-caption/tree/main}) is utilized for data generation. Given a molecule, predict its point group.
\subparagraph{SMILES-IUPAC}
Web scrapped \gls{smiles} \gls{iupac} pairs from the PubChem database \cite{pubchem} and then framed questions involve converting \gls{smiles} notation to \gls{iupac} nomenclature, utilizing information from the PubChem database.

@@

\subparagraph{Number of isomers}
We used MAYGEN\cite{Yirik_2021} to compute the number of isomers for a set of randomly sampled SMILES from the ZINC dataset.
To obtain the answers for false options we sampled from the set of number of isomers.

>>>>

\subparagraph{Analytical chemistry}
The questions are based on master student examination papers at the University of Jena (Germany). 
These questions focus on the principles and techniques employed in analytical chemistry.

\subparagraph{Combustion engineering}
These questions are based on master student examination papers at the University of Magdeburg (Germany). 
They explore topics related to combustion processes and engineering principles.

\subparagraph{Functional materials and nanomaterials}
The questions based on exercises in a seminar conducted at the University of Jena (Germany), delving into topics concerning functional materials and nanomaterials, exploring their properties and applications.

\subparagraph{General chemistry}
The questions originate from examinations for grade 10 at Marist Comprehensive Academy Uturu (Nigeria). 
They cover fundamental concepts in chemistry suitable for students at the secondary school level.
In addition, we included questions based on the general chemistry courses of the Bachelor of Science in Chemistry at the Technical University of Munich (Germany).

\subparagraph{International Chemical Olympiad (\gls{ICHO})}
The questions are based on various countries' Chemical Olympiads, including those held in the USA, UK, and Moldova.

\subparagraph{Material synthesis}
These questions are based on seminars on material synthesis at the University of Jena (Germany), focusing on the methods and techniques employed in the synthesis of various materials.

\subparagraph{Organic reactivity}
The questions are primarily sourced from tutorials and exam papers at for the Bachelor of Science in Chemistry at the Technical University of Munich (Germany), exploring reactions and mechanisms in organic chemistry.

\subparagraph{Periodic table}
The questions are manually created to cover various aspects and trends of the periodic table.

\subparagraph{Polymer chemistry}
Questions are based on examinations held at the University of Hamburg (Germany), covering topics related to polymer chemistry and its applications.

@@

\subparagraph{Chemical safety}
This category comprises a total of 4792 questions, covering areas such as GHS classification, hazard statements, \gls{dai}, and pictograms from the PubChem database \cite{pubchem}, contributing 976 questions. 
Additionally, it explores crucial topics like materials' compatibility, with 3200 questions, essential for understanding the hazardous impact of mixing certain materials and chemicals. 
Furthermore, it includes inquiries about the Federal/State Working Group on Chemical Safety (BLAC), consisting of 90 questions. These questions are based on the question bank used for the \enquote{Sachkundeprüfung} (expertise examination) according to \§ 11 of the \enquote{Chemikalien-Verbotsverordnung} (Chemical Prohibition Ordinance).
Moreover, this category addresses questions related to chemical storage and compatibility, totaling 297 questions, and covers topics such as pharmacology, toxicology, material safety data sheets, and chemical safety data sheets. 
The chemical safety category stands out as one of the primary focus areas within the \chembench corpus.

@@

\subparagraph{Oxidation states}
The questions regarding oxidation states are extracted from the website \url{https://www.cheminfo.org/}. 
These exercises focus on determining the number of isomers for specific molecules. To perform these calculations, we utilize the RDKit package \cite{rdkit}.

\subparagraph{Electron count of atoms}
Questions pertaining to the electron count of atoms are gathered from the website \url{https://www.cheminfo.org/}. 
These inquiries involve determining the electron count of atoms in various chemical contexts. The calculations for these tasks are facilitated using the RDKit package \cite{rdkit}.

\subparagraph{Number of isomers}
The questions concerning the number of isomers are sourced from the website \url{https://www.cheminfo.org/}. 
These exercises aim to determine the number of isomers for given molecules. The calculations for these assessments are conducted using the RDKit package \cite{rdkit}.

\subparagraph{Point group for molecules}
Questions involve predicting the point group for molecules. The ChemCaption tool (\url{https://github.com/lamalab-org/chem-caption/tree/main}) is utilized for data generation. Given a molecule, predict its point group.
\subparagraph{SMILES-IUPAC}
Web scrapped \gls{smiles} \gls{iupac} pairs from the PubChem database \cite{pubchem} and then framed questions involve converting \gls{smiles} notation to \gls{iupac} nomenclature, utilizing information from the PubChem database.

@@

\subparagraph{Number of isomers}
We used MAYGEN\cite{Yirik_2021} to compute the number of isomers for a set of randomly sampled \gls{smiles} from the ZINC dataset.\cite{Irwin_2012}
To obtain the answers for false options we sampled from the set of number of isomers.
